---
title: "Problem 2"
author: "Yufei Yin"
output: pdf_document
---

# Problem 2
Make a new figure with 1 column and 1 row, then define 'radius' as a vector of length 10,000. These small increments will make the plot look like a smooth curve instead of a choppy set of lines. By now all of your plots should be properly labelled. Full points are only for well made plots. Have you had this error yet?
`Error in plot.new() : figure margins too large' If so you need to make the plot window larger in RStudio. 

## Question 2a, (4 points): 

Provide a .pdf of this new plot. 

## Question 2b, (1 point): 

provide the R code you used to make it. 

## Question 2c, (1 bonus point): 

make a version of this plot using the R package ggplot2 (https://cran.r-project.org/web/packages/ggplot2/ggplot2.pdf) and provide a .pdf of the plot. You may need to read about installing the ggplot2 package using the command install.packages.

```{r}
par(mfrow=c(1,1))
radius = seq(from = 1, to = 7, length = 10000)
volume = 4/3*pi*radius^3
plot(radius,volume,main="Volume vs. Radius",
     xlab="radius",
     ylab="volume",
     xlim=c(0,8),
     ylim=c(0,1500),
     col = 'red')
```

```{r}
# Question 2c
library(ggplot2)
df = data.frame(radius,volume)
ggplot(data = df, aes(x = radius, y = volume)) + 
  geom_point(color = "red") + 
  ggtitle("Volumn vs. Radius") +
  xlim(0,8)
```
