---
title: "Problem4"
author: "Yufei Yin"
output: pdf_document
---

# Problem 4

## Question 4a, (2 points): 
Find the names of the Pokemon which are taller then 2 meters and are Legendary.                                                 

(Hint: it's usually wise to first extract several columns of data to make sure your code does what you think it does.) 

Provide these names with one name per line.


```{r, echo=FALSE}
poke = read.csv(file = "D:/Simon Fraser University/2021 spring/STAT 240/Labs/lab1/pokemon_2019.csv",header=TRUE,sep = ",")
```

```{r}
poke[poke$Height_m > 2 & poke$isLegendary == "True","Name"]
```

## Question 4b, (6 points): 
Let's extract two body styles of Pokemon. We'll restrict this question to just pokemon with two body styles: 'head_arms' and 'serpentine_body'. 

Plot the Attack vs Defense of any Pokemon that has those body style (with 'head arms' on the x axis and 'serpentine body' on the y axis). 

Upload a .pdf of this plot. 

Hint: it's usually wise to first extract several columns of data to make sure your code does what you think it does. Here especially as you are using compound criteria.

```{r}
sub_poke = poke[,c("Attack","Defense","Body_Style")]
df = sub_poke[sub_poke$Body_Style == "head_arms" | sub_poke$Body_Style == "serpentine_body",]
head_arms = sub_poke[sub_poke$Body_Style == "head_arms",]
serpentine_body = sub_poke[sub_poke$Body_Style == "serpentine_body",]
plot(df$Attack, df$Defense,
     main = "Defense vs. Attack",
     xlab = "Attack",
     ylab = "Defense",
     xlim = c(0,150),
     ylim = c(0,210))
points(head_arms, col="red")
points(serpentine_body, col="blue")
legend(x = "topleft", col = c("red","blue"), pch = c(1,1), c("head arms", "serpentine body"))
```



