---
title: "Question 2"
author: "Yufei Yin"
output: pdf_document
---

# Question 2

* Further modify your code so that instead of initializing the cluster assignments of the data items randomly, instead assign data item i to cluster ((i-1)%%K)+1. (i.e., if K = 3 and there are 7 data items, the initialization assigns the data items in order to 1, 2, 3, 1, 2, 3, 1).

*Run this further modified version of kmedians on the parkinsons dataset with K = 3, and iters = 1000. Report the locations of the 3 clusters.

```{r}
kmedians = function(x, k, iters){
  N = dim(x)[1] 
  D = dim(x)[2] 
  
  centres = matrix(NA, k, D)
  clusters = rep(NA, N)
  
  for (i in 1:N){
    clusters[i] = ((i-1) %% k)+1
  }
  
  for (iter in 1:iters){
    for (k in 1:k){
      for (d in 1:D){
        centres[k, d] = median(x[clusters == k, d]) 
      }
    }
    distanceMatrix <- matrix(NA, nrow=N, ncol=k)
    for(i in 1:k) {
      distanceMatrix[,i] <- rowSums(t(abs(t(x)-centres[i,])))
    }
    clusters <- apply(distanceMatrix, 1, which.min)
    centres <- apply(x, 2, tapply, clusters, median)
  }
  return(list(locations=centres, assignment=clusters))
}
```

```{r}
data = read.table(file = 'parkinsons.data', sep = ',', header = TRUE)
data = data[,-1]
res = kmedians(x = data, k = 3, iters = 1000)
res$locations
```

